---
title: "Rprog"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

suggest going to the help for read.pdb to see what is inside the pdb object

```{r}
ids <- c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")
#selecting chains _A or _B when we say split = TRUE
files <- get.pdb(ids, split = TRUE)
```

```{r}
source("https://bioconductor.org/biocLite.R")
biocLite("muscle")
```


```{r}
pdbs <- pdbaln(files, fit = TRUE) #pdbaln superimposes all chains together
pdbs
```

VMD also lists what you selected in the command prompt



